When are Fuzzy Extractors Possible?

### 2014-07-15 info-bounds/FuzzyExtPossibility.tex
editing

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
\]
\end{definition}
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  In the interactive setting, fuzzy min-entropy is also a sufficient condition using secure two-party computation\bnote{cite something for this}.  However, in the non-interactive setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.  We attempt to bridge this gap in this work.

\section{Well-spread distributions}
In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.  We begin by considering secure sketches.  We a call distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Intuitively, no sketch should be necessary for such a distribution.  However, we show there is a large gap between a secure sketch that works for a particular well-spread distribution and a secure sketch that works for \emph{all} well-spread distributions.

\begin{table}
\begin{tabular}{l | l | c}
Upper bound & Depends on Distribution & Works for all Dist\\
\hline
Well-spread distribution & $0$ & $\log |B_t|$\\
Flat distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta)$ &$\log |B_t|$\\
Arbitrary distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta) + \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\caption{Upper bounds on minimum number of bits that a fuzzy extractor can write down and still have recovery.}
\label{tab:upper bounds}
\end{table}
\subsection{Distribution Dependent Sketches}
Error-correction should be easy when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.  Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  We begin by defining a well-spread distribution.

@@

\subsection{Distribution Agnostic Sketches}
Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).  It is not known if it is necessary to decrease the entropy of the distribution $W$.

\begin{lemma}
Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.  Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.  Then the length of $\sketch$ is at least $\log |B_{t}|$.
\end{lemma}
\begin{proof}
Let $\mathcal{M}$ be a metric space.
Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
Consider the following experiment:
\[
W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
\]
That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.   Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.  Now consider the following experiment
\[
v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
\]
Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.  Then $X\overset{d}= Y$.  That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.  Thus, $\Pr[v^* = v] = 1$.  For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.  For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.  Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.  This completes the proof.
\end{proof}
\noindent
\textbf{Note:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.  The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).

@@

\section{Flat spread distributions}
In the previous section we showed bounds on producing secure sketches and fuzzy extractors for well-spread distributions.  In this section we further investigate secure sketches where the sketch depends on the input distribution.\footnote{Recall the bound when the sketch does not know the input distribution is $\log |B_t|$ bits and this is constructible for any distribution.}

\subsection{Distribution Dependent Sketches}

@@

\bnote{need to extend this to a non-fixed number of bits and randomized.}
\section{Dealing with non flat distributions}
The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.

Dealing with non-flat distributions requires a new strategy.  Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.  We first a natural method to leverage convex combinations that does not work\bnote{phrasing}.  We then show a solution that comes within \bnote{something} of optimal by partitioning the probability space.

\subsection{Leveraging convex combinations?}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following extension to \consref{cons:pairwise hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, we show it is difficult to leverage convex combinations in the finite setting and handling the infinite case is more difficult.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.

@@

Consider an input point $w\in W$.  One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.  It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.  For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.  This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.  This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.  Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.  In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.

\begin{figure}[h]

@@

\bnote{remove pagebreak later}

\subsection{Layered Hashing}
As we saw in the previous section, dealing with non-flat distributions is difficult.  The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.  We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.  Then the hash is applied only considering the maximum weight of the ball containing points at this level.  Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.

\pagebreak

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
Let $\epsilon>0$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=k,..., n+\log 1/\epsilon$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.  We describe $\sketch, \rec$ as follows:
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-n}/\epsilon$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

Before describing the bounds obtained by \consref{cons:leveling} we will extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without epsilon.  I found the expression to be really gross with $\epsilon$ included.  Thoughts?  I know $\epsilon$ needs to be there because the construction uses it.}
\begin{proof}
We begin by arguing correctness.  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-n}\epsilon$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.  Now consider the case when $\Pr[W=w]> 2^{-n}\epsilon$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

>>>>

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
\]
\end{definition}
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  In the interactive setting, fuzzy min-entropy is also a sufficient condition using secure two-party computation\bnote{cite something for this}.  However, in the non-interactive setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.  We attempt to bridge this gap in this work.

\section{Well-spread distributions}
In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.  We begin by considering secure sketches.  We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Intuitively, no sketch should be necessary for such a distribution.  However, we show there is a large gap between a secure sketch that works for a particular well-spread distribution and a secure sketch that works for \emph{all} well-spread distributions.

\begin{table}
\begin{tabular}{l | l | c}
Upper bound & Depends on Distribution & Works for all Dist\\
\hline
Well-spread distribution & $0$ & $\log |B_t|$\\
Flat distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta)$ &$\log |B_t|$\\
Arbitrary distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta) + \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\caption{Upper bounds on minimum number of bits that a secure sketch can write down and still recovery with overwhelming probability.}
\label{tab:upper bounds}
\end{table}
\subsection{Distribution-Dependent Sketches}
Error-correction should be easy when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.  Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  We begin by defining a well-spread distribution.

@@

\subsection{Distribution-Agnostic Sketches}
Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.  The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.  We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.  The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.

We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).

\begin{lemma}
Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.  Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.  Then the average length of $\sketch$ is at least $\log |B_{t}|$.
\end{lemma}
\bnote{what do we mean by average here?  we mean when receiving a uniform input across the coins.  Maybe, there are distributions where it writes down a little.  What's the right thing to say?  Markov?}
\begin{proof}
Let $\mathcal{M}$ be a metric space.
Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
Consider the following experiment:
\[
W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
\]
That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.   Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.  Now consider the following experiment
\[
v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
\]
Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.  Then $X\overset{d}= Y$.  That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.  Thus, $\Pr[v^* = v] = 1$.  For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.  For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.  Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.  This completes the proof.
\end{proof}
\noindent
\textbf{Notes:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.  The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).

@@

The above lemma only talks about how many bits the algorithms must write down.  It does not say that the entropy of the distribution must decrease~(this is the important question).

\section{Flat distributions}
In the previous section we showed bounds on producing secure sketches and fuzzy extractors for well-spread distributions.  In this section we further investigate secure sketches where the sketch depends on the input distribution.\footnote{Recall the bound when the sketch does not know the input distribution is $\log |B_t|$ bits and this is constructible for any distribution.}

\subsection{Distribution-Dependent Sketches}

@@

\section{Arbitary distributions}
The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.

Dealing with non-flat distributions requires a new strategy.  Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.  We first consider a mechanism that tries to reduce the arbitrary case to the flat case by selecting a candidate flat distribution.  Unfortunately, this mechanism does not work as a distribution with high fuzzy min-entropy can be formed as a convex combination of distributions with almost no fuzzy min-entropy~(\secref{sec:convex comb}).

We then show a solution that comes within a super-logarithmic factor of optimal of optimal by partitioning the probability space~(\secref{sec:layered hash}).

\subsection{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.

@@

Consider an input point $w\in W$.  One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.  It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.  For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.  This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.  This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.  Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.

\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.  However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.  That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.

In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.

\begin{figure}[t]

@@

\subsection{Layered Hashing}
\label{sec:layered hash}
In the previous section, we saw that sketching non-flat distributions is difficult~(while retaining entropy close to the fuzzy min-entropy).  The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.  We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.  Then the hash is applied only considering the maximum weight of the ball containing points at this level.  Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.  Naturally, revealing the probability of the original point leaks some information and there is a balance between how much about the probability is revealed to the adversary and how useful it is.

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.  We describe $\sketch, \rec$ as follows: 
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

Before describing the bounds obtained by \consref{cons:leveling} we will extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions but this is not necessary.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
